\section*{Author and Contact Information}
\begin{itemize}
  \item Written by: \href{https://github.com/JaiNasu}{\emph{Jai Nasu}}
  \item Contact: \href{https://discordapp.com/users/475766542181859331}{\emph{Discord Account}}
\end{itemize}

\section*{Preface}

This is a introductory text for preliminaries of particle physics and covers the basics of:
\begin{itemize}
  \item Analytical Mechanics
  \item Field Theory
  \item Special Relativity
  \item Quantum Mechanics
  \item Some Mathematics
  \item Extra topics
\end{itemize}

The intended audience is from a motivated high school student to a 1st/ 2nd year undergraduate student, who want a sneak peak/ a birds-eye view of what particle physics is about.
I am working on this document as a personal study material and a reference for myself, so I can refer to it when I need to.
I will likely be updating this document later, so if you find any mistakes, please let me know.

Most of the content is very basic, so if you really want to dig into each subject, I strongly recommend that you read actual textbooks on each subjects.
Some good/ known textbooks in English are listed at the end, so make sure to check them out. I would like to hear some suggestions too!

If you have any questions, please feel free to contact me via Discord, or through Github.
I will try to answer/ fix any issues as it could be a good learning experience for myself too.

Lastly, Extra topics are kind of a miscellaneous section, where I put some topics that I find interesting, but redundant/ not necessary for the main content. You can skip them if you want.

